% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Enrique Noriega-Atala}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {machine learning, statistics, computer science, artificial intelligence},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.unc.edu/}{The University of Arizona} \\
  School of Information \\
  Tucson, AZ 85719
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +1 (520) 241-5945 \\
    %Fax: &  (919) 962-5678 \\
    Email: & \href{mailto:enrique.noriega@gmail.com}{\tt enrique.noriega@gmail.com} \\
    Homepage: & \href{https://enoriega.info/}{\tt https://enoriega.info/} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}
%
%\begin{itemize}
%\item Born on September 29, 1895.
%\item United States Citizen.
%\end{itemize}


\section*{Education}

\begin{itemize}
  \item \textbf{Ph.D. Information Science}, The University of Arizona (expected summer 2019). \\
     \textbf{- Minor:} Statistics
  \item \textbf{M.S. Computer Science}, The University of Arizona (2014).
  \item \textbf{B.S. Information Technologies}, Monterrey Institute of Technology and Higher Education (2010).
\end{itemize}


\section*{Professional Experience}

\begin{itemize}
\item \textbf{2013 - present} Graduate Research Associate, The University of Arizona (UA)
\item \textbf{2013 - present} Teaching Assistant, UA. Courses:
\item \begin{itemize}
	\item Computer Organization (2013)
	\item Data Structures (2014)
	\item Information Retrieval and Web Search (2015, 2016)
	\item Introduction to Machine Learning (2017)
\end{itemize}
\item \textbf{2012 - present} Software Development Consulting, Fresh Software Concepts LLC (FSC)
\item \textbf{2010 - 2012} Sr Software Developer, FSC
\item \textbf{2009 - 2010} Software Developer, Teknol, SA de CV
\item \textbf{2008 - 2009} Internship at {\small Centro de Investigaci\'{o}n y Desarrollo de Ingenier\'{i}a Avanzada, AC}
\item \textbf{2007 - 2008} Web Developer, Optima Commerce LLC
\end{itemize}

\section*{Research Interests}
Machine Learning, Reinforcement Learning, Natural Language Processing, Artificial Intelligence, Statistics.

\section*{Honors and Awards}
\begin{itemize}
	\item UA Graduate \& Professional Student's Council Travel Grant (2018).
	\item UA School of Information's Travel Award (2018).
	\item International Conference in Data Mining Student Award (2018).
	\item Galileo Circle Scholar, UA's College of Science (2014).
	\item Instituto Educativo Sonora-Arizona scholarship (2013-2014).
	\item CONACyT graduate studies scholarship (2012-2014).
	\item CENEVAL's outstanding performance testimony on the EGEL test (2010). 
\end{itemize}


\section*{Presentations and Publications}

\subsection*{Journal Publications}
\begin{itemize}
	\item \textbf{Enrique Noriega-Atala}, Paul D. Hein, Shraddha S. Thumsi, Zechy Wong, Xia Wang, Sean M. Hendryx, Clayton T. Morrison\\ Extracting Inter-sentence Relations for Associating Biological Context with Events in Biomedical Text. \textit{IEEE/ACM transactions on computational biology and bioinformatics. 2019.}
	\item Marco A. Valenzuela-Esc\'{a}rcega, \"{O}zg\"{u}n Babur, Gus Hahn-Powell, Dane Bell, Thomas Hicks, \textbf{Enrique Noriega-Atala}, Xia Wang, Mihai Surdeanu, Emek Demir, Clayton T. Morrison. \\ Large-scale Automated Machine Reading Discovers New Cancer Driving Mechanisms. \textit{Database: The Journal of Biological Databases and Curation. 2018.} 
\end{itemize}

\subsection*{Conference Publications}
\begin{itemize}
\item \textbf{Enrique Noriega-Atala}, Marco A. Valenzuela-Esc\'{a}rcega, Clayton T. Morrison and Mihai Surdeanu. Learning what to read: Focused machine reading. \textit{Proceedings of the Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2017.
\end{itemize}

\subsection*{Workshop Publications}
\begin{itemize}
	\item \textbf{Enrique Noriega-Atala}, Marco A. Valenzuela-Esc\'a{a}rcega, Clayton T. Morrison and Mihai Surdeanu. Focused Reading: Reinforcement Learning for What Documents to Read. \textit{Proceedings of the Interactive Machine Learning and Semantic Information Retrieval Workshop at ICML, 2017.}
	\item Marco A. Valenzuela-Esc\'{a}rcega, \"{O}zg\"{u}n Babur, Gus Hahn-Powell, Dane Bell, Thomas Hicks, \textbf{Enrique Noriega-Atala}, Xia Wang, Mihai Surdeanu, Emek Demir, Clayton T. Morrison. \\Large-scale Automated Reading with Reach Discovers New Cancer Driving Mechanisms. \textit{Proceedings of the BioCreative VI Workshop} (BioCreative6 2017), 2017, pp. 200-202.
	\item \textbf{Enrique Noriega-Atala}, Paul D. Hein, Shraddha S. Thumsi, Zechy Wong, Xia Wang, Clayton T. Morrison. \\ Inter-sentence Relation Extraction for Associating Biological Context with Events in Biomedical Texts. \textit{Proceedings of the Sixth Workshop on Data Mining in Biomedical Informatics and Healthcare at ICDM, 2018.}
	\item \textbf{Enrique Noriega-Atala}, Zhengzhong Liang, John A. Bachman, Clayton T. Morrison, Mihai Surdeanu.\\ Understanding the Polarity of Events in the Biomedical Literature: Deep Learning vs. Linguistically-informed Methods. \textit{Proceedings of the Workshop on extracting structured knowledge from scientific publications at NAACL-HLT, 2019.} (In Press) 

\end{itemize}

\subsection*{Conference Presentations}

\begin{itemize}
	
\item Learning what to read: Focused machine reading. \textit{NLP Applications track, EMNLP}, Copenhagen, Denmark (2017).
\item Grounding Gradable Adjectives through Crowd-sourcing \textit{Language Resources and Evaluation Conference}, Miyazaki, Japan (2018).
\item Inter-sentence Relation Extraction for Associating Biological Context with Events in Biomedical Text. \textit{Sixth Workshop on Data Mining in Biomedical Informatics and Healthcare at ICDM}, Singapore (2018).
\end{itemize}

\subsection*{Guest Lectures}
\begin{itemize}
	\item What is Machine Learning?. For the course \textit{Knowledge-based Systems in the Organizations. Systems and Industrial Engineering program}. Monterrey Institute of Technology and Higher Education, Hermosillo, M\'{e}xico (2015).
\end{itemize}


\section*{Skills}
\subsection*{Programming Languages:}
\begin{itemize}
	\item Python, Scala, Java, C\#, C, C++, JavaScript, VB.NET
\end{itemize}


\subsection*{Systems administration}
\begin{itemize}
	\item Unix-like environment proficiency.
	\item Bash scripting.
	\item Relational DBMS (SQL Server, Postgres, MySQL) and NoSQL experience (Redis, Neo4J).
	\item Cloud computing environment experience with Azure and AWS.
\end{itemize}

\section*{Open Source Software}
\begin{itemize}
	\item SARSAmora: A Reinforcement Learning library for Scala (\url{https://github.com/ml4ai/SARSAmora})
\end{itemize}
\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    %\href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
